Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-08-03 doc/ms.tex
Update the author list for the paper

% \author{A.~A.~Miller}
% \affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
% \affil{The Adler Planetarium, Chicago, IL 60605, USA}
%
% \author[0000-0002-8036-8491]{Yi Cao}
% \affil{eScience Institute and Astronomy Department, University of Washington,
%   Seattle, WA 98195}
% \affil{Google, Mountain View, CA 94043, USA}
%
% \author{B.~D.~Bue}
% \affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}

% \author{R.~Ferretti}
% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{A.~Goobar}
% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{G.~Hosseinzadeh}
% \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
% \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
%
% \author{M.~M.~Kasliwal}
% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
%
% \author{R.~R.~Laher}
% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
%
% \author{F.~J.~Masci}
% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
%
% \author{P.~E.~Nugent}
% \affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
% \affil{University of California -- Berkeley, Berkeley, CA 94720, USA}
%
% \author{J.~Sollerman}
% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{F.~Taddia}
% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{S. R. Kulkarni}
% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
%
\author{The Alphabet Friends}
\affil{the intermediate Palomar Transient Factory}

@@

\begin{itemize}
    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $\sim$0.2 d after the time of first light.

    \item The early emission from \abc\ is powered solely by radioactive $^{56}$Ni decay. We find no evidence for detectable signatures of SN shock cooling or the collision of the SN ejecta with a non-degnerate binary companion.

\item The velocity evolution of the SN ejecta shows that the time of explosion is approximately equal to the time of first light. This constitutes the first major piece of evidence that $^{56}$Ni is strongly mixed into the outer layers of the supernova ejecta.

\item The strong and short-lived carbon features seen in the 
earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion and there is a non-thermal 
radiation source in the outermost layers of the ejecta to excite the ionized carbon. $^{56}$Ni decay is the likely source of the non-thermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.

@@

\end{itemize}
%
Taken together, these observations all indicate that the nucleosynthetic products from the explosion are well mixed throughout the SN ejecta. There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times. In the future, it would be useful to investigate PDD models that incorporate strong $^{56}Ni$ mixing to see if they better replicate the observations of \abc.

>>>>

\author[0000-0001-9515-478X]{A.~A.~Miller}
\affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
\affil{The Adler Planetarium, Chicago, IL 60605, USA}

\author[0000-0002-8036-8491]{Y.~Cao}
\affil{eScience Institute and Astronomy Department, University of Washington,
  Seattle, WA 98195}
\affil{Google, Mountain View, CA 94043, USA}

\author[0000-0001-6806-0673]{A.~L.~Piro}
\affil{The Observatories of the Carnegie Institution for Science, 813 Santa Barbara Street, Pasadena, CA 91101, USA}

\author{B.~D.~Bue}
\affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}

\author[0000-0003-1673-970X]{S.~B.~Cenko}
\affil{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}
\affil{NASA Goddard Space Flight Center, Mail Code 661, Greenbelt, MD 20771, USA}

\author{R.~Ferretti}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

\author[0000-0003-2238-1572]{O.~D.~Fox}
\affil{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

\author{A.~Goobar}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{G.~Hosseinzadeh}
\affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
\affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
\affil{LSSTC Data Science Fellow}

\author{M.~M.~Kasliwal}
\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}

\author{R.~R.~Laher}
\affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}

\author{R.~Lunnan}
\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}

\author{F.~J.~Masci}
\affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}

\author{P.~E.~Nugent}
\affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\affil{University of California -- Berkeley, Berkeley, CA 94720, USA}

\author{J.~Sollerman}
\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{F.~Taddia}
\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}

\author{S. R. Kulkarni}
\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}

% \author{The Alphabet Friends}
% \affil{the intermediate Palomar Transient Factory}

@@

\begin{itemize}
    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only 0.15 d after the time of first light.

    \item We find no evidence for detectable signatures of SN shock cooling or the collision of the SN ejecta with a non-degnerate binary companion.

    \item Assuming that $v_\mathrm{photosphere} \propto t^{-0.22}$, the time of explosion is approximately equal to the time of first light. A short ``dark period,'' as this implies, is likely the result of either strong $^{56}$Ni mixing or interaction of the SN ejecta with diffuse material.

    \item The strong and short-lived carbon features seen in the 
earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion. The pulsational delayed detonation models presented in \citet{2014MNRAS.441..532D} produce \ion{C}{2} absorption that is as strong as \ion{Si}{2} at very early phases.

    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2 d after first light. Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over our first $\sim$7 d  of observations.

@@

\end{itemize}
%
Taken together, these observations all indicate that the nucleosynthetic products from the explosion are well mixed throughout the SN ejecta. There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times. In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing and interaction with diffuse material, but the simulations presented in those studies do not replicate all of the salient features of \abc.}
